---
title: "p8105_hw1_jw4007"
output: github_document
date: "2022-09-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1

```{r penguins}
data("penguins", package = "palmerpenguins")
penguins
nrow(penguins)
ncol(penguins)
mean_flipper = mean(penguins$flipper_length_mm, na.rm = TRUE)
flipper_vs_bill = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

flipper_vs_bill

ggsave("flipper_vs_bill.png")
```

This data set includes the following variables: `r colnames(penguins)`. 

There are `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r round(mean_flipper, digits=2)`mm.

## Problem 2
```{r hw1_df}
hw1_df = tibble(
  random_sample = rnorm(10),
  logical_vec = random_sample > 0,
  character_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("low", "low", "low", "mid", "mid", "mid", "high", "high", "high", "high"))
)

hw1_df

mean_samp = mean(pull(hw1_df, random_sample))
mean_logical = mean(pull(hw1_df, logical_vec))
mean_character = mean(pull(hw1_df, character_vec))
mean_factor = mean(pull(hw1_df, factor_vec))

```
The mean of the random sample is `r round(mean_samp, digits = 2)`.

The mean of the logical vector is `r round(mean_logical, digits = 2)`.

The mean of the character vector is `r round(mean_character, digits = 2)` and the mean of the factor vector is `r round(mean_factor, digits = 2)`. These two cannot be taken mean because they are neither numeric nor logical.

```{r, echo=TRUE, results='hide'}

character_num = as.numeric(pull(hw1_df, character_vec))
factor_num = as.numeric(pull(hw1_df, factor_vec))

character_num 
factor_num

mean(character_num)
mean(factor_num) 
```
After using "as.numeric", the mean for the factor vector could be produced, but not the mean for the character vector. The reason is that the factor vector becomes a collection of 1, 2, and 3 after conversion but the character vector does not becomes number. This explain why the mean for the character vector still cannot be taken.



